My title

### 2024-03-12 paper/paper.qmd
Edits

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

@@

```{r}
#| label: fig-vote
#| fig-cap: ""
#| echo: false
#| eval: true
#| warning: false
#| message: false

>>>>

Define $y_i$ as the ... Then $\beta_i$ is the ... and $\gamma_i$ is the ...

@@

We expect a positive relationship between .... In particular...

@@

```{r}
#| label: fig-vote
#| fig-cap: "The distribution of presidential preferences, by gender, and highest education"
#| echo: false
#| eval: true
#| warning: false
#| message: false
